%% Master CV - Pham Hai Nam
%% Comprehensive overview of all competencies, experience, and projects.
%% Use as a master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%%
%% Populated by /setup on 2026-07-15.
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Pham Hai Nam - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Pham Hai}{Nam}
\address{Ha Noi, Vietnam}{}{}
\phone[mobile]{0346294259}
\email{namphamhai7@gmail.com}
\extrainfo{\href{https://github.com/phamnam2003}{github.com/phamnam2003}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Backend engineer with around two years building production Go services (Gin, gRPC, Worker Pool, dependency injection with uber-go/dig and Fx) across fintech and public-sector systems. Owned architecture and database modeling end to end on a real-estate lead platform and a document-AI system for the Ministry of Public Security. Comfortable designing event-driven microservices with Kafka, Redis, and PostgreSQL, and standing up the observability and CI/CD around them (OpenTelemetry, Prometheus/Grafana/Loki, GitHub Actions, ArgoCD). Also ships the React/Next/Vue frontends that consume these APIs.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Go backend}: Gin, gRPC (mutual TLS, interceptors, streaming), Worker Pool, dependency injection (uber-go/dig, Fx); RESTful APIs and microservices; unit and integration testing.

\item \textbf{Distributed \& event-driven}: Apache Kafka and RabbitMQ messaging, Redis (cache, pub/sub, streams), Asynq, Ristretto; asynchronous import/export pipelines and background processing.

\item \textbf{Data}: PostgreSQL (incl. PostGIS), MySQL, Oracle, SQLite, MongoDB, ScyllaDB/Cassandra; database modeling and transaction management; sqlc for type-safe queries.

\item \textbf{Infrastructure \& observability}: Docker, Kubernetes (Calico, Cilium, Envoy Gateway, Nginx Ingress); OpenTelemetry, Prometheus, Grafana, Loki; GitHub Actions, GitLab Runners, ArgoCD; object storage (MinIO, SeaweedFS, S3-compatible).

\item \textbf{Frontend}: TypeScript/JavaScript with ReactJS, Next.js, Vue.js; Redux, Redux Toolkit, Recoil; Tailwind CSS, Ant Design.

\item \textbf{Security \& AI-assisted development}: PASETO, TOTP/2FA, TLS/mTLS and crypto fundamentals; Claude Code, GitHub Copilot, and Spec-Kit spec-driven workflows.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\needspace{5\baselineskip}
\item{\cventry{11/2025--Present}{Frontend and Backend Developer}{AIONtech}{Ha Noi, Vietnam}{}{\vspace{1pt}
\begin{itemize}
    \item Implemented dependency injection with uber-go/dig and Fx to improve scalability and maintainability of Go backend services.
    \item Refactored and optimized internal packages to improve performance and strengthen application safety.
    \item Built background processing with Redis Pub/Sub and Apache Kafka for event-driven business workflows.
    \item Contributed to the design of scalable software systems and architectures.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\needspace{5\baselineskip}
\item{\cventry{06/2024--10/2025}{Frontend and Backend Developer}{Leeon Group}{Ha Noi, Vietnam}{}{\vspace{1pt}
\begin{itemize}
    \item Took ownership of an inherited production Go codebase from departing team members; maintained, debugged, and enhanced projects wired into CI/CD.
    \item Implemented messaging and caching: RabbitMQ, Redis (cache/pub-sub/streams), Ristretto, and the Worker Pool pattern for background tasks.
    \item Worked with gRPC in depth (mutual TLS, metadata, interceptors, streaming); secured services with SSL/TLS certificates in Docker.
    \item Stood up the observability stack: Prometheus, Grafana, Loki, and OpenTelemetry for unified traces, metrics, and logs.
    \item Built ReactJS web applications with Tailwind CSS and Ant Design.
\end{itemize}}}

\vspace{3pt}

% --- Earlier Role ---
\needspace{5\baselineskip}
\item{\cventry{07/2023--02/2024}{Full-stack Developer}{TLGEO}{Ha Noi, Vietnam}{}{\vspace{1pt}
\begin{itemize}
    \item Built UIs with Vue.js and Next.js; developed and consumed APIs with ExpressJS and Strapi.
    \item Contributed to system design using PostgreSQL with the PostGIS extension for spatial data; used Mapbox for government mapping and agriculture projects.
    \item Handled deployment on Linux/Ubuntu Server with SSH and Nginx.
\end{itemize}}}

\vspace{3pt}

% --- Oldest Role ---
\needspace{5\baselineskip}
\item{\cventry{04/2023--06/2023}{Frontend Intern}{Lalasoft}{Ha Noi, Vietnam}{}{\vspace{1pt}
\begin{itemize}
    \item Applied Redux Core, Redux Toolkit, and Ant Design to ongoing company projects.
    \item Researched and built small internal tools as Chrome Extensions.
\end{itemize}}}

\end{itemize}

% ============================================================
%     SELECTED PROJECTS
% ============================================================

\section{Selected Projects}
\vspace{3pt}
\begin{itemize}

\needspace{4\baselineskip}
\item{\cventry{03/2026--Present}{SkyReality --- Real-estate lead platform}{Backend Developer, team of 7}{}{}{\vspace{1pt}
\begin{itemize}
    \item Architected the system: database modeling and backend stack decisions.
    \item Integrated webhook event processing from Zalo, Slack, and Telegram bots; implemented OAuth2 Google Sign-In and multipart upload with checksum verification.
    \item Stack: Go (Gin), Kafka, Redis, PostgreSQL, uber-go/dig.
\end{itemize}}}

\vspace{3pt}

\needspace{4\baselineskip}
\item{\cventry{11/2025--01/2026}{Sacombank Smart Teller Machine (STM)}{Backend Developer, team of 8}{}{}{\vspace{1pt}
\begin{itemize}
    \item Built asynchronous import/export pipelines and added step-level transaction logging across STM workflows.
    \item Resolved duplicate-data issues and removed background-processing bottlenecks; applied dependency injection for testability.
    \item Stack: Go (Gin), Kafka, Oracle, SQLite, Prometheus, Grafana, Docker.
\end{itemize}}}

\vspace{3pt}

\needspace{4\baselineskip}
\item{\cventry{12/2025--Present}{Document AI for C06, Ministry of Public Security}{Backend Developer, team of 9}{}{}{\vspace{1pt}
\begin{itemize}
    \item Architected the system: database modeling and backend stack decisions for an AI document-summarization and task-generation platform.
    \item Stack: Go (Gin), Kafka, PostgreSQL, Python, Docker, Kubernetes.
\end{itemize}}}

\vspace{3pt}

\needspace{4\baselineskip}
\item{\cventry{Open source}{github.com/phamnam2003}{Go references \& study repos}{}{}{\vspace{1pt}
\begin{itemize}
    \item gRPC reference built from the protocol up (all four method types, interceptors, insecure/TLS/mTLS); \texttt{challenges} repo with 20 Gang-of-Four patterns and 18+ algorithm solutions in Go; \texttt{go-2fa} TOTP implementation.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\needspace{3\baselineskip}
\item{\cventry{2021--2026}{Engineer's degree, Information Technology}{Hanoi Open University (HOU)}{Ha Noi, Vietnam}{}{\vspace{1pt}
Software engineering, data structures \& algorithms, databases, computer networks, web development.
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Vietnamese (native); English (professional working --- technical reading and writing).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
